---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggiplot

<!-- badges: start -->
[![R-CMD-check](https://github.com/grantmcdermott/ggiplot/actions/workflows/check-release.yaml/badge.svg)](https://github.com/grantmcdermott/ggiplot/actions/workflows/check-release.yaml)
[![R-universe status badge](https://grantmcdermott.r-universe.dev/badges/ggiplot)](https://grantmcdermott.r-universe.dev)
[![Docs](https://img.shields.io/badge/docs-homepage-blue.svg)](https://grantmcdermott.com/ggiplot/index.html)
[![R-CMD-check](https://github.com/grantmcdermott/ggiplot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/grantmcdermott/ggiplot/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package provides a **ggplot2** equivalent of the base 
[`fixest::iplot()`](https://lrberge.github.io/fixest/reference/coefplot.html)
function. The primary goal of **ggiplot** is convenient and
aesthetically-pleasing 
[event study](https://theeffectbook.net/ch-EventStudies.html) plots.

## Installation

The package is not yet on CRAN, but can be installed from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("grantmcdermott/ggiplot")
```
## Quickstart

A detailed
[introductory vignette](http://grantmcdermott.com/ggiplot/articles/ggiplot.html) 
with many examples is provided on the package homepage (or, by typing 
`vignette("ggiplot")` in your R console). But here are a few quickstart examples
to whet your appetite. First, a basic event study plot.

```{r example1, message=FALSE}
library(ggiplot)
library(fixest)

est_did = feols(y ~ x1 + i(period, treat, 5) | id+period, base_did)

# iplot(est_did) ## base version
ggiplot(est_did) ## this package
```

The above plot call and output should look very familiar to regular **fixest**
users. But note that `ggiplot()` supports several features that are not 
available in the base `iplot()` version. For example, plotting multiple 
confidence intervals and aggregate treatments effects.

```{r example2}
ggiplot(
	est_did,
	ci_level = c(.8, .95),
	aggr_eff = "post", aggr_eff.par = list(col = "orange")
	)
```

And you can get quite fancy, combining lists of complex multiple estimation
objects with custom themes, and so on.

```{r example3}
base_stagg_grp = base_stagg
base_stagg_grp$grp = ifelse(base_stagg_grp$id %% 2 == 0, 'Evens', 'Odds')

est_twfe_grp = feols(
	y ~ x1 + i(time_to_treatment, treated, ref = c(-1, -1000)) | id + year,
	data = base_stagg_grp, split = ~grp
	)

est_sa20_grp = feols(
	y ~ x1 + sunab(year_treated, year) | id + year, 
	data = base_stagg_grp, split = ~grp
	)

ggiplot(list('TWFE' = est_twfe_grp, 'Sun & Abraham (2020)' = est_sa20_grp),
        ref.line = -1,
        main = 'Staggered treatment: Split mutli-sample',
        xlab = 'Time to treatment',
        multi_style = 'facet',
        geom_style = 'ribbon',
				facet_args = list(labeller = labeller(id = \(x) gsub(".*: ", "", x))),
        theme = theme_minimal() +
					theme(
						text = element_text(family = 'HersheySans'),
						plot.title = element_text(hjust = 0.5),
						legend.position = 'none'
						)
				)
```


## License

The material in this repository is made available under the 
[MIT license](http://opensource.org/licenses/mit-license.php).
