---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggiplot

<!-- badges: start -->
<!-- badges: end -->

This package provides a **ggplot2** equivalent of the base 
[`fixest::iplot()`](https://lrberge.github.io/fixest/reference/coefplot.html)
function.

[`Installation`](#installation) | [`Examples`](#examples) | [`License`](#license)

## Installation

Install from [GitHub](https://github.com/):

``` r
# install.packages("remotes")
remotes::install_github("grantmcdermott/ggiplot")
```
## Examples

Here follow some examples that draw on the **fixest** 
[introductory vignette](https://lrberge.github.io/fixest/articles/fixest_walkthrough.html),
as well as the `iplot()` help documentation. 

As we'll see, the package essentially consists of a single function &mdash; 
**`ggiplot()`** &mdash; that tries to closely mimic it base compatriot. However, 
by leveraging the **ggplot2** API and infrastructure, it also offers some 
additional functionality.

Start by loading the **ggiplot** package alongside **fixest**.

```{r example, message=FALSE}
library(ggiplot)
library(fixest)
```

### Example 1: Vanilla TWFE

```{r est_did}
data(base_did)
base_inter = base_did

est_did = feols(y ~ x1 + i(period, treat, 5) | id+period, base_inter)
```

Let's compare the (base) `iplot` and `ggiplot` default plots.

```{r est_did_plot_defaults}
iplot(est_did)
ggiplot(est_did)
```

There are some small differences, but they are certainly producing the same
basic plot. To get even closer to the original, we could specify the use of 
errorbar(s) rather than (`ggiplot`'s default of) pointrange(s).

```{r est_did_ebar}
ggiplot(est_did, geom = 'errorbar')
```

Many of the arguments for `iplot()` carry over to `ggiplot()` too. This is
deliberate, since we want to reduce the cognitive overhead of switching between
the two plotting methods. For example, we can join points using the same 
`pt.join = TRUE` argument.

```{r est_did_pt_join}
iplot(est_did, pt.join = TRUE)
ggiplot(est_did, pt.join = TRUE, geom_style = 'errorbar')
```

The `ggiplot` defaults are slightly different in some cases, but may require
less arguments depending on what you want to do. For example,

```{r est_did_ribbon}
# iplot(est_did, pt.join = TRUE, ci.lty = 0, ci.width = 0, ci.fill = TRUE)
iplot(est_did, pt.join = TRUE, ci.lty = 0, ci.width = 0, ci.fill = TRUE,
      ci.fill.par = list(col = 'black', alpha = 0.4))
ggiplot(est_did, geom_style = 'ribbon')
ggiplot(est_did, geom_style = 'ribbon', pt.pch = NA, col = 'orange')
```

### Example 2: Multiple estimation (i)

We'll demonstrate using the staggered treatment example from the **fixest**
introductory vignette.

```{r base_stagg}
data(base_stagg)
est_twfe = feols(y ~ x1 + i(time_to_treatment, treated, ref = c(-1, -1000)) | 
								 	id + year, base_stagg)
est_sa20 = feols(y ~ x1 + sunab(year_treated, year) | 
								 	id + year, base_stagg)
```

Again, for comparison, here the base `iplot` original. Note that we add the 
legend manually.

```{r stagg_iplot}
iplot(list('TWFE' = est_twfe, 'Sun & Abraham (2020)' = est_sa20),
      main = 'Staggered treatment', ref.line = -1, pt.join = TRUE)
legend('topleft', col = c(1, 2), pch = c(20, 17),
			  legend = c('TWFE', 'Sun & Abraham (2020)'))
```

Here's the `ggiplot` version.

```{r stagg_ggiplot}
ggiplot(list('TWFE' = est_twfe, 'Sun & Abraham (2020)' = est_sa20),
        main = 'Staggered treatment', ref.line = -1, pt.join = TRUE)
```

If we don't name out list of models then it defaults to something sensible.

```{r stagg_ggiplot_noname}
ggiplot(list(est_twfe, est_sa20),
        main = 'Staggered treatment', ref.line = -1, pt.join = TRUE)
```

One nice thing about the **ggplot2** API is that it makes changing multiplot
figures simple. For example, if you don't like the presentation of "dodged" 
models in a single frame, then it's easy to facet them instead using 
the `multi_style = 'facet'` argument.

```{r stagg_ggiplot_facet}
ggiplot(list('TWFE' = est_twfe, 'Sun & Abraham (2020)' = est_sa20),
        main = 'Staggered treatment', ref.line = -1, pt.join = TRUE,
        multi_style = 'facet')
```

### Example 3: Multiple estimation (ii)

An area where `ggiplot` shines is in complex multiple estimation cases, such
as lists of `fixest_multi` objects. To illustrate, let's add a split variable
(group) to our staggered dataset.

```{r base_stagg_grp}
base_stagg_grp = base_stagg
base_stagg_grp$grp = ifelse(base_stagg_grp$id %% 2 == 0, 'Evens', 'Odds')
```

Now re-run our two regressions from earlier, but splitting the sample to
generate `fixest_multi` objects.

```{r stagg_grp}
est_twfe_grp = feols(y ~ x1 + i(time_to_treatment, treated, ref = c(-1, -1000)) | 
										 	id + year, base_stagg_grp, 
										 split = ~ grp)
est_sa20_grp = feols(y ~ x1 + sunab(year_treated, year) | 
										 	id + year, base_stagg_grp, 
										 split = ~ grp)
```

Both `iplot` and `ggiplot` do fine with a single `fixest_multi` object (although
remember that we have to manually add a legend for the former)

```{r stagg_grp_single}
iplot(est_twfe_grp, ref.line = -1, main = 'Staggered treatment: TWFE')
legend('topleft', col = c(1, 2), pch = c(20, 17),
			  legend = c('Evens', 'Odds'))
ggiplot(est_twfe_grp, ref.line = -1, main = 'Staggered treatment: TWFE')
```

However, `iplot` complains if we combine a list of _several_ `fixest_multi` 
objects.

```{r stagg_grp_multi_iplot, error = TRUE}
iplot(list('TWFE' = est_twfe_grp, 'Sun & Abraham (2020)' = est_sa20_grp),
      ref.line = -1, main = 'Staggered treatment: Split mutli-sample')
```

In contrast, `ggiplot` works...

```{r stagg_grp_multi_ggiplot}
ggiplot(list('TWFE' = est_twfe_grp, 'Sun & Abraham (2020)' = est_sa20_grp),
        ref.line = -1, main = 'Staggered treatment: Split mutli-sample')
```

... but is even better when we use faceting instead of dodged errorbars.
Let's use this an opportunity to construct a fancy plot that invokes some
additional arguments and ggplot theming.

```{r stagg_grp_multi_ggiplot_fancy}
ggiplot(list('TWFE' = est_twfe_grp, 'Sun & Abraham (2020)' = est_sa20_grp),
        ref.line = -1,
        main = 'Staggered treatment: Split mutli-sample',
        xlab = 'Time to treatment',
        multi_style = 'facet',
        geom_style = 'ribbon',
        theme = theme_minimal() +
           theme(text = element_text(family = 'HersheySans'),
                 plot.title = element_text(hjust = 0.5),
                 legend.position = 'none'))
```


### Asides 

#### On theming and scale adjustments

Setting the theme inside the `ggiplot()` call is optional and not strictly
necessary, since the ggplot2 API allows programmatic updating of existing
plots. E.g.

```{r theme_update}
last_plot() + labs(caption = 'Note: Super fancy plot brought to you by ggiplot')
last_plot() + 
	theme_grey() + 
	theme(legend.position = 'none') +
	scale_colour_brewer(palette = 'Set1', aesthetics = c('colour', 'fill'))
```

etc.

#### On dictionaries

Dictionaries work similarly to `iplot`. Simple example:

```{r dict}
base_inter$letter = letters[base_inter$period]
est_letters = feols(y ~ x1 + i(letter, treat, 'e') | id+letter, base_inter)

# Dictionary for capitalising the letters
dict = LETTERS[1:10]; names(dict) = letters[1:10]

ggiplot(est_letters) # No dictionary
```

You can either set the dictionary directly in the plot call...

```{r dict_direct}
ggiplot(est_letters, dict = dict)
```

... Or, set it globally using the `setFixest_dict()` macro.

```{r dict_global}
setFixest_dict(dict)
ggiplot(est_letters)

setFixest_dict() # reset
```

## License

The material in this repository is made available under the 
[MIT license](http://opensource.org/licenses/mit-license.php).
